Title

### 2017-11-30 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
Doing the figures for macrolunch presentation
Not completed yet
added the last plot to macro lunch presentation

@@

	Why has TFP slowed down? % show TFP graph here

@@

@@

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{IT investment: a break at the right time}
	\label{it_investment}

>>>>

	Why has TFP slowed down?

@@

	\vspace{-1cm}
	\noindent
	\begin{figure}
		\centering
		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_TFP_macrolunch_29-Nov-2017_17_41_17}
	\end{figure}

@@

		\vspace{-1cm}
	\noindent
	\begin{figure}
		\centering
		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_RD_macrolunch_29-Nov-2017_18_12_20}
	\end{figure}

@@

	\vspace{-1cm}
	\noindent
	\begin{figure}
		\centering
		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_RD_level_macrolunch_29-Nov-2017_18_28_54}
	\end{figure}

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{IT investment: a drop at the right time}
	\label{it_investment}

%	\vspace{-1cm}
	\noindent
	\begin{figure}
		\centering
		\includegraphics[scale=0.31]{\ourFigPath Figures/fig_IT_level_macrolunch_30-Nov-2017_10_06_45}
	\end{figure}
